DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
experiments: graphs, NN architectures, hyper-params, and cleanup of SHREC'17 and ModelNet40 appendix

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
	\item figure placements
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
\end{itemize}
}
\newpage

@@

\paragraph{Convolution.}
On Euclidean domains, convolutions are efficiently implemented by sliding a window in the signal domain.
On the sphere however, there is no straightforward way to implement a convolution in the signal domain due to non-uniform samplings.
Convolutions are most often performed in the spectral domain through a spherical harmonic transform (SHT).
That is the approach taken by \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn}, which has a computational cost of $\bO(n^{3/2})$ on isolatitude pixelizations (such as the HEALPix and equiangular grids) and $\bO(n^2)$ in general.
On the other hand, following \citet{defferrard2016graphnn}, graph convolutions can be defined as
\begin{equation} \label{eqn:graph_conv}
	h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f},
\end{equation}
where $K$ is the polynomial order (which corresponds to the filter's size) and $\alpha_i$ are the coefficients to be optimized during training.
Those convolutions are used by \citet{khasanova2017sphericalcnn} and \citet{perraudin2019deepspherecosmo} and cost $\bO(n)$ operations through a recursive application of $\b{L}$.\footnote{As long as the graph is sparsified such that the number of edges, i.e., the number of non-zeros in $\b{A}$, is proportional to the number of vertices $n$. This can always be done as most weights are very small.}

@@

\paragraph{Architecture.}
All our NNs are fully convolutional, and employ a global average pooling (GAP) for rotation invariant tasks.
Graph convolutional layers are always followed by batch normalization and ReLU activation, except in the last layer.
Note that batch normalization and activation act on the elements of $\b{f}$ independently, and hence don't depend on the domain of $f$.
%We denote graph convolutional layers with $C$ output channels as $GC_C$ and fully connected layers with $C$ output neurons as $FC_C$.
%Those linear layers are always followed by batch normalization and ReLU activation, except in the last layer.
%softmax normalization as $SM$
%Pooling and unpooling by a factor $F$ are denoted as $P_F$ and $P^{-1}_F$, global average pooling as $GAP$.

@@

\subsection{Finding the optimal set of weights}

% 1) summary the work of Khasanova
\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

@@

% 2) explain our approach
We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eq:belkin_weights}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}

\begin{table}
    \centering
	%\begin{tabular}{l cc r rr}
	\begin{tabular}{l cc r rS[table-format=2.0]}
		\toprule
		& \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
		& F1 & mAP & params & \multicolumn{1}{c}{inference} & \multicolumn{1}{c}{training} \\
		\midrule
		% $SO(3)$ vs $S^2$ vs graph
		\citet{cohen2018sphericalcnn} ($b=128$) & 78.9 & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.6 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
		\bottomrule
	\end{tabular}
    \caption{
		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
		% F1-score computed with sklearn, mAP from the official script of the competition.
		% inference speed = time for a single instance to do a single training pass
		% training speed = time for the neural net to train to peak performance
	}
    \label{tab:shrec17}
\end{table}
\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}

@@

Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
Those parameters are typically estimated by likelihood-free inference, which requires a function to predict the parameters from simulations.
% such as Approximate Bayesian computation (ABC)
As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps ($1/12 \approx 8\%$ of the sphere) made of $n \approx 10^6$ pixels from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
% 60 maps * 12 parts = 720 parts
Convergence maps represent the distribution of over- and under-densities of mass in the universe \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}

@@

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}

@@

Compared to \citet{cohen2019gauge}'s conclusion, it is surprising that S2R does worse than DeepSphere (which is limited to S2S).
Potential explanations are (i) that their icosahedral projection introduces harmful distortions, or (ii) that a larger architecture can compensate for the lack of generality. % powerfulness?
We indeed observed that more feature maps and depth led to higher performance (\ref{sec:climate:appendix}).

@@

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}

@@

* Network architecture and training details

\subsection{3D object Recognition}
\subsubsection*{Detailed results}
\paragraph*{SHREC17}

\begin{table}
    \centering
    \begin{tabular}{l|c c r r}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.9ms & 47m \\
        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 0.9ms & 46m\\
        % DeepSphere \emph{Improved HEALPix} & 80.76 & & &
    \end{tabular}
    \caption{Performance of different models}
    \label{tab:SHREC17_class}
\end{table}

\begin{table}
    \centering
    \begin{tabular}{l|c c c c|c c c c}
     & \multicolumn{4}{c|}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
    Method & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\ \hline
    Cohen \emph{s2cnn} & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
    % Cohen \emph{s2cnn\_simple} & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385\\
    Esteves \emph{sphericalcnn} & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444\\ \hline
    DeepSphere \emph{Equiangular} & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
    DeepSphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428\\
    % DeepSphere \emph{Improved HEALPix} & & & & &
    \end{tabular}
    \caption{Performance of different models over SHREC17 perturbed dataset as a retrieval task, using the official script of the competition.}
    \label{tab:SHREC17_retriev}
\end{table}

\paragraph*{ModelNet 40}

\begin{table}
    \centering
    \begin{tabular}{c|cccc}
         &  x/x & z/z & SO3/SO3 & z/SO3 \\ \hline
Cohen & 85.0 & - & - & - \\
Jiang & 90.5 & - & - & - \\
Esteves \emph{scnn} & - & 88.9 & 86.9 & 78.6 \\
%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
DeepSphere & 87.8 & 86.8 & 86.7 & 76.9
    \end{tabular}
    \caption{Accuracy (in percent) on test set, for different models. The x dataset has no augmentation, the z dataset is augmented with rotation around Z-axis, and SO3 with ZYZ rotations.}
    \label{tab:mn40_results}
\end{table}

\subsubsection*{HEALPix architecture}

HEALPix sampling, input signal at Nside = 32

CNN having 5 convolutional layers, a global average pooling layer and a fully-connected layer at the end, such as this:
\begin{dmath}
    [GC_{16}\, +\, BN\, +\, ReLU]_{nside32}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{nside16}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{nside8}\, +\, \textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{nside4}\, +\,\textrm{Pool}\, +\, [GC_{256}\, +\, BN\, +\, ReLU]_{nside2}\, +\, \textrm{Pool}\, +\, GAP\, +\, FCN\, +\, \textrm{softmax}
\end{dmath}
Each convolutional layer has a graph convolution using Chebyshev polynomial approximation, batch normalization and ReLU activation. The order of the Chebyshev polynomial is 4 for each layer, the number of feature maps are [16, 32, 64, 128, 256] respectively and down-sampling to the immediate smaller resolution for each layer.

number of parameter: 190k TODO exact number?

batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
cross-entropy loss, and add triplet loss from ``Esteves et al.''

30 epochs with augmented dataset, 3 random translation perturbation (same as 90 epochs over dataset with 3 possible random rotation)
\subsubsection*{Equiangular architecture}
Equiangular sampling with bandwidth of 64 in longitude and latitude.
The architecture of the Neural Network is exactly the same, with a stride of [2, 2] for each pooling layer
\subsection{cosmo}
HEALPix sampling, Nside = 1024, with improved graph

@@

The order of the Chebyshev polynomial is 5 for each layer, the number of feature maps are [16, 32, 64, 64, 64, 3] respectively and down-sampling to the immediate smaller resolution for each layer.

batch size = 8, 80 epochs, adam optimizer, cross-entropy loss, learning rate $2\cdot10^{-4}\cdot0.999^{\textrm{step}}$

@@

@@

batch size 1
\subsection{GHCN}
non-regular sampling, thus no pooling was used

batch size 64, RMSprop optimizer, constant learning rate of $1 \cdot 10{-3}$, MSE loss, order of 5 for all layers

250 epochs with no augmentation

\subsubsection*{Deatilled results}

\subsubsection*{Dense task architecture}

\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{1}]
\end{dmath}

\subsubsection*{Global task architecture}

\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, GAP\, +\, FCN
\end{dmath}

>>>>

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
	\item figure placements
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
	\item shall we still site adam and batch norm?
	\item check results on ModelNet40
\end{itemize}
}
\newpage

@@

\paragraph{Convolution.}
On Euclidean domains, convolutions are efficiently implemented by sliding a window in the signal domain.
On the sphere however, there is no straightforward way to implement a convolution in the signal domain due to non-uniform samplings.
Convolutions are most often performed in the spectral domain through a spherical harmonic transform (SHT).
That is the approach taken by \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn}, which has a computational cost of $\bO(n^{3/2})$ on isolatitude pixelizations (such as the HEALPix and equiangular grids) and $\bO(n^2)$ in general.
On the other hand, following \citet{defferrard2016graphnn}, graph convolutions can be defined as
\begin{equation} \label{eqn:graph_conv}
	h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f},
\end{equation}
where $K$ is the polynomial order (which corresponds to the filter's size) and $\alpha_i$ are the coefficients to be optimized during training.\footnote{In practice, training with Chebyshev polynomials (instead of monomials) is slightly more stable. We believe it to be due to their orthogonality and uniformity.}
Those convolutions are used by \citet{khasanova2017sphericalcnn} and \citet{perraudin2019deepspherecosmo} and cost $\bO(n)$ operations through a recursive application of $\b{L}$.\footnote{As long as the graph is sparsified such that the number of edges, i.e., the number of non-zeros in $\b{A}$, is proportional to the number of vertices $n$. This can always be done as most weights are very small.}

@@

\paragraph{Architecture.}
All our NNs are fully convolutional, and employ a global average pooling (GAP) for rotation invariant tasks.
Graph convolutional layers are always followed by batch normalization \citep{ioffe2015batchnorm} and ReLU activation, except in the last layer.
Note that batch normalization and activation act on the elements of $\b{f}$ independently, and hence don't depend on the domain of $f$.
%We denote graph convolutional layers with $C$ output channels as $GC_C$ and fully connected layers with $C$ output neurons as $FC_C$.
%Those linear layers are always followed by batch normalization and ReLU activation, except in the last layer.
%softmax normalization as $SM$
%Pooling and unpooling by a factor $F$ are denoted as $P_F$ and $P^{-1}_F$, global average pooling as $GAP$.

@@

\subsection{Finding the optimal set of weights}  \label{sec:optimal}

% 1) summary the work of Khasanova
\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eqn:weights:khasanova}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

@@

% 2) explain our approach
We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

The equiangular graph is built with \eqnref{weights:khasanova} and $k = 4$ neighbors \citep[following][]{khasanova2017sphericalcnn}.
\todo{The HEALPix graph is built with \eqnref{weights:belkin}, $k = ?$ and the corresponding optimal kernel width $t = ?$.}
\todo{Following Esteves or Cohen?}
The NN is made of $5$ graph convolutional layers, each followed by a \todo{max?} pooling layer down-sampling by $4$.
A GAP and a fully connected layer with softmax follow.
The Chebyshev polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
Following \citet{esteves2018sphericalcnn}, the cross-entropy plus a triplet loss is optimized with Adam \citep{kingma2014adam} for 30 epochs on the dataset augmented by 3 random translations.
The learning rate is $5 \cdot 10^{-2}$ and the batch size is 32.

\begin{table}
    \centering
	%\begin{tabular}{l cc r rr}
	\begin{tabular}{l cc r rS[table-format=2.0]}
		\toprule
		& \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
		& F1 & mAP & params & \multicolumn{1}{c}{inference} & \multicolumn{1}{c}{training} \\
		\midrule
		% $SO(3)$ vs $S^2$ vs graph
		\citet{cohen2018sphericalcnn} ($b=128$) & - & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.9 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
		\bottomrule
	\end{tabular}
    \caption{
		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
		% F1-score computed with sklearn, mAP from the official script of the competition.
		% inference speed = time for a single instance to do a single training pass
		% training speed = time for the neural net to train to peak performance
	}
    \label{tab:shrec17}
\end{table}
\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}

@@

Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
Those parameters are typically estimated by likelihood-free inference, which requires a function to predict the parameters from simulations.
% such as Approximate Bayesian computation (ABC)
As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
% 60 maps * 12 parts = 720 parts
Convergence maps represent the distribution of over- and under-densities of mass in the universe \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.

Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ and the corresponding optimal kernel widths $t = ?, ?, ?$.
Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a \todo{max?} pooling layer down-sampling by $4$.
A GAP and a fully connected layer with softmax follow.
The Chebyshev polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
The cross-entropy loss is optimized with Adam for 80 epochs.
The learning rate is $2 \cdot 10^{-4} \cdot 0.999^{\textrm{step}}$ and the batch size is 8.

@@

The graph is built with \eqnref{weights:belkin}, \todo{$k = ?$} and the \todo{corresponding optimal kernel widths $t = ?, ?, ?$}.
Following \citet{jiang2019sphericalcnn}, the NN is an encoder-decoder with skip connections.
Details in \secref{climate:appendix}.
%The encoder is made of $5$ graph convolutional layers, each followed by a \todo{pick-one?} pooling layer down-sampling by $4$.
%the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
%The decoder is made of
The Chebyshev polynomials are all of \todo{order $K=5$}.
The cross-entropy loss (weighted or non-weighted) is optimized with Adam for 30 epochs.
The learning rate is $1 \cdot 10{-3}$ and the batch size is 64.

@@

Compared to \citet{cohen2019gauge}'s conclusion, it is surprising that S2R does worse than DeepSphere (which is limited to S2S).
Potential explanations are (i) that their icosahedral projection introduces harmful distortions, or (ii) that a larger architecture can compensate for the lack of generality. % powerfulness?
We indeed observed that more feature maps and depth led to higher performance (\secref{climate:appendix}).

@@

The graph is built with \eqnref{weights:khasanova} and \todo{$k = ?$} neighbors.
The kernel width $t$ is set as the average of the distances.
The equivariance property of the resulting graph has not been tested, and we don't expect it to be good due to the heavily non-uniform sampling.
The NN is made of $3$ graph convolutional layers.
The Chebyshev polynomials are all of order $K=0$ or $4$ and the number of channels per layer is $50, 100, 100$, respectively.
For the global regression, a GAP and a fully connected layer follow.
For the dense regression, a graph convolutional layer follows instead.
The MSE loss is optimized with RMSprop for 250 epochs.
The learning rate is $1 \cdot 10^{-3}$ and the batch size is 64.

@@

\subsection{3D objects recognition}

\Tabref{shrec17_retrieval} shows the results obtained from the competition's official evaluation script.
\Tabref{modelnet40} shows results on ModelNet40.

\begin{table}
    \centering
	\scriptsize
    \begin{tabular}{l cccc cccc}
    & \multicolumn{4}{c}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
	\cmidrule(lr){2-5} \cmidrule(lr){6-9}
    & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\
	\toprule
    \citet{cohen2018sphericalcnn} ($b=128$) & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
    \citet{cohen2018sphericalcnn} (simplified, $b=64$) & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385 \\
    \citet{esteves2018sphericalcnn} ($b=64$) & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444 \\
    DeepSphere (equiangular $b=64$) & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
    DeepSphere (HEALPix $N_{side}=32$) & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428\\
	\bottomrule
    \end{tabular}
    \caption{Official metrics from the SHREC'17 object retrieval competition.}
    \label{tab:shrec17_retrieval}
\end{table}

\begin{table}
    \centering
    \begin{tabular}{l cccc}
	\toprule
    & no/no & z/z & SO3/SO3 & z/SO3 \\
	\midrule
	\citet{cohen2018sphericalcnn} & 85.0 & - & - & - \\
	\citet{jiang2019sphericalcnn} & 90.5 & - & - & - \\
	\citet{esteves2018sphericalcnn} & - & 88.9 & 86.9 & 76.7 \\
	%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
	DeepSphere & 87.8 & 86.8 & 86.7 & 76.9 \\
	\bottomrule
    \end{tabular}
    \caption{
		Accuracy results on ModelNet40.
		``no'' denotes no augmentation, ``z'' is augmented with rotations around the Z-axis, and ``SO3'' with ZYZ rotations.
		\todo{The first is training time augmentation, the second test time augmentation.}
	}
    \label{tab:modelnet40}
\end{table}

\begin{dmath}
    [GC_{16}\, +\, BN\, +\, ReLU]_{nside32}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{nside16}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{nside8}\, +\, \textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{nside4}\, +\,\textrm{Pool}\, +\, [GC_{256}\, +\, BN\, +\, ReLU]_{nside2}\, +\, \textrm{Pool}\, +\, GAP\, +\, FCN\, +\, \textrm{softmax}
\end{dmath}

\subsection{Cosmological model classification}

@@

@@

\Tabref{climate:accuracy}, \ref{tab:climate:map}, and \ref{tab:climate:speed} show the accuracy, mAP, and efficiency of all the NNs we ran.

@@

batch size 1

\subsection{Uneven sampling}

Architecture for dense regression:
\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{1}]
\end{dmath}

Architecture for global regression:
\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, GAP\, +\, FCN
\end{dmath}
